Function multiversioning in system image

### 2017-10-17 presentations/2017-10-17_julia-mv/present.tex
[presentations/2017-10-17_julia-mv] WIP

\documentclass{beamer}
\mode<presentation>{
  \usetheme{Boadilla}
  \usefonttheme[onlylarge]{structurebold}
  \usefonttheme[stillsansseriflarge]{serif}
  \setbeamerfont*{frametitle}{size=\normalsize,series=\bfseries}
  % \setbeamertemplate{navigation symbols}{}
  \setbeamercovered{transparent}
}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{esint}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{multimedia}
\usepackage{bm}
\usepackage{siunitx}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

@@

% \def\timeleft{15:00->14:55}

\title[Na ground state cooling]{Raman sideband cooling of a single sodium atom to 3D ground state}
\date{April 19, 2017}
\author[Yichao Yu]{Yichao Yu\\
  \vspace{0.5cm}
  {\footnotesize Lee Liu, Dr. Nick Hutzler,\\
    Jessie Zhang, Dr. Jon Hood}}
\institute{Ni Group/Harvard}

@@

% \begin{frame}{}
%   \tableofcontents
% \end{frame}

\begin{frame}{}
  \begin{center}
    \begin{tikzpicture}
      \visible<1> {
        \path (0, 0) node
        {\includegraphics[width=10cm]{../2015-05-05_cua/overall_full_min.png}};
      }
      \visible<2-> {
        \path (0, 0) node
        {\includegraphics[width=10cm]{../2015-05-05_cua/overall_trap_min.png}};
        \path (3, -3) node
        {\includegraphics[width=3cm]{../../experiments/nacs_atoms/imgs/single_viridis.png}};
      }
    \end{tikzpicture}
  \end{center}
\end{frame}

\begin{frame}{Wave function size mismatch}
  \begin{center}
    \begin{tikzpicture}
      \shade[ball color=blue!90] (0, 0) circle (0.45);
      \shade[ball color=orange!90] (0.4, 0.2) circle (0.3);
      \draw[<->,line width=1] (-0.45, 0.4) -- (0.35, 0.8);
      \path (-0.05, 0.6) node[rotate=26.565,above=2pt] {$4a_0$};
      \path (0.2, -2) node[below] {\textbf{Molecule}};

      \draw[line width=1] plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {(\x)^2 * 0.8 - 1.5});
      \draw[line width=2,orange!90!black]
      plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {exp(-(\x)^2 * 1.3) - 0.988});
      \draw[line width=0.8] (6 - 0.8, -0.988) -- (6 + 0.8, -0.988);
      \draw[<->,line width=1] (6 - 1, 0.3) -- (6 + 1, 0.3);
      \path (6, 0.3) node[above] {$1000a_0$};
      \path (6, -2) node[below] {\textbf{Atom}};
    \end{tikzpicture}
    \vspace{1cm}
    \begin{block}{Goal of cooling}
      \begin{itemize}
      \item Single initial state
      \item Shrink wavefunction size
      \end{itemize}
    \end{block}
  \end{center}
\end{frame}

\begin{frame}{Raman sideband cooling of Sodium}
  \begin{columns}
    \column{6.5cm}
    \includegraphics[width=6cm]{Na_RSC_schematic.pdf}
    \column{5cm}
    \visible<2->{
      \begin{block}{Difficulties}
        \begin{itemize}
        \item High initial temperature ($40\mu K$)
        \item<3-> High recoil heating\\
          {\footnotesize (High Lamb Dicke parameter)}
        \end{itemize}
      \end{block}
    }
  \end{columns}
\end{frame}

\begin{frame}{Raman sidebands}
  \begin{center}
    \begin{tikzpicture}
      \visible<1> {
        \path (0, 0) node {
          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2_before.png}
        };
        \draw[<-, line width=1.5] (-0.7, 0) -- (0, 1.6) node[right] {\Large Carrier};
      }
      \visible<2> {
        \path (0, 0) node {
          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2.png}
        };
      }
      \visible<3> {
        \path (0, 0) node {
          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3.png}
        };
      }
    \end{tikzpicture}
  \end{center}
\end{frame}

\begin{frame}{Raman sidebands}
  \begin{center}
    \begin{tikzpicture}[scale=1.41176]
      \visible<1> {
        \path (0, 0) node {
          \includegraphics[width=12cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1_before.png}
        };
        \draw[red, <-, line width=1.5] (-3.15, 0.5) -- (-2.95, 1.2)
        node[above right] {\Large 1st order heating};
        \draw[<-, line width=1.5] (-2.45, 0.2) -- (-2.25, 0.8) node[above right] {\Large Carrier};
        \draw[black!40!green, <-, line width=1.5] (-1.7, 0.2) -- (-1.55, 0.6)
        node[right] {\Large 1st order cooling};
        \draw[blue, <-, line width=1.5] (-0.95, -0.1) -- (-0.55, 0.1)
        node[right] {\Large 2nd order cooling};
        \path[magenta] (0.25, -0.5) node[right] {\Large And higher orders{$\cdots$}};
      }
      \visible<2-> {
        \path (0, 0) node {
          \includegraphics[width=12cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1.png}
        };
      }
      \visible<3-> {
        \fill[white,opacity=0.95] (-4.2, -2.5) rectangle (5, 2.5);
        \path (0, 1) node[align=center]
        {
          \begin{tabular}{|c|c|}
            \hline
            \textbf{Axis}&\textbf{Ground state probability}\\\hline
            1 (Axial)&93.1(2.5)\%\\\hline
            2 (Radial)&91.9(2.3)\%\\\hline
            3 (Radial)&92.9(2.5)\%\\\hline
          \end{tabular}
        };
        \visible<4-> {
          \path (0, -1) node[align=center]
          {
            \textbf{3D ground state:} $79.5(3.6)\%$\\
            \textbf{Loss after cooling:} $15\%$\\\\
            \textbf{Total 3D ground state preparation fidelity:} $67.6(3.1)\%$
          };
        }
      }
    \end{tikzpicture}
  \end{center}
\end{frame}

\begin{frame}{Rabi flopping (radial)}
  \begin{center}
    \visible<+->{
      \includegraphics[width=10cm]{../../experiments/rabi_flop/imgs/fit_20170409_r2_0_ba.png}\\
    }
    \visible<+->{
      Good agreement in ground state probability between spectrum and Rabi flopping data.
    }
  \end{center}
\end{frame}

\begin{frame}{Rabi flopping (axial)}
  \begin{center}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_nol.png}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_nol.png}
  \end{center}
\end{frame}

\begin{frame}{}
  \begin{block}{Conclusion}
    $67.6(3.1)\%$ ground state preparation fidelity {\small ($79.5(3.6)\%$ without loss)}
  \end{block}
  \vspace{1cm}
  \begin{block}{Improvements}
    \begin{itemize}
    \item Reduce off-resonance scattering from Raman beams
    \item Reduce magnetic field fluctuation
    \item Reduce loss during cooling
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{}
\end{frame}

\begin{frame}{Axial matrix element}
  \begin{center}
    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.43_0-6}.png}
  \end{center}
\end{frame}

\begin{frame}{Radial 2 matrix element}
  \begin{center}
    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.35_0-2}.png}
  \end{center}
\end{frame}

\begin{frame}{Radial 3 matrix element}
  \begin{center}
    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.29_0-2}.png}
  \end{center}
\end{frame}

>>>>

\documentclass{beamer}
\mode<presentation>{
  \usetheme{Boadilla}
  \usefonttheme[onlylarge]{structurebold}
  \usefonttheme[stillsansseriflarge]{serif}
  \setbeamerfont*{frametitle}{size=\normalsize,series=\bfseries}
  % \setbeamertemplate{navigation symbols}{}
  \setbeamercovered{transparent}
}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{esint}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{multimedia}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

@@

\title{Function multiversioning in system image}
\subtitle{All about vector registers}
\date{Oct. 16, 2017}
\author{Yichao Yu}
\institute{Harvard}

@@

\begin{frame}{}
  \begin{center}
    \includegraphics[width=11cm]{imgs/pr21849.png}
  \end{center}
\end{frame}

% Probably more techincal and low level than many other talks
% So let's set the base line
% By Jameson

% With that in mind, feel free to ask questions.

% I'll talk less about this PR specifically,
% but more about the general issue when dealing with code compiled for different architectures.

\begin{frame}{Goal}
  \visible<+-> {
    \begin{block}{Amount of implementation details}
      \begin{itemize}
      \item<+-> Just enough to make Jeff happy
      \item<+-> Without losing the audience
      \item<+-> With a single version of the talk \textbf{(Important!)}
      \end{itemize}
    \end{block}
  }
\end{frame}

% Story
% * openlibm performance issue

\begin{frame}{How did it all begin}
  \begin{tikzpicture}
    \node at (0, 0) {\includegraphics[width=11cm]{imgs/issue17395.png}};
    \visible<2>{
      \fill[white,opacity=0.85] (5.5, 3.9) rectangle (-5.5, -3.9);
      \node[fill=red!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (-4, 2) (S1) {Startup};
      \node[fill=red!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (2, 2) (S2) {Slow loop};

      \node[fill=green!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (-4, -2) (F2) {Magic};
      \node[fill=green!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (2, -2) (F3) {Fast loop};
      \draw[->, line width=1.4] (S1) edge (S2) (S2) edge (F2) (F2) edge (F3);

      \node at (3, 0) (L0) {Same code};

      \draw[->, gray, line width=1] (L0) edge (S2);
      \draw[->, gray, line width=1] (L0) edge (F3);

      \draw[<-, line width=1.4] (S2.north) arc(190:-80:0.9);
      \draw[<-, line width=1.4] (F3.south) arc(-190:80:0.9);
    }
  \end{tikzpicture}
\end{frame}

\begin{frame}{Register size}
  \begin{center}
    \begin{tikzpicture}
      \node at (-4, 2) (ax) {\textbf{ax}};
      \node at (-2, 2) (eax) {\textbf{eax}};
      \node at (0, 2) (rax) {\textbf{rax}};

      \node at (0, 1.3) (mmx0) {\textbf{mmx0}};
      \node at (2, 1.3) (xmm0) {\textbf{xmm0}};
      \node at (4, 1.3) (ymm0) {\textbf{ymm0}};
      \node at (6, 1.3) (zmm0) {\textbf{zmm0}};

      \draw[->, line width=1, gray] (ax) edge (eax);
      \draw[->, line width=1, gray] (eax) edge (rax);
      \draw[->, line width=1, gray] (mmx0) edge (xmm0);
      \draw[->, line width=1, gray] (xmm0) edge (ymm0);
      \draw[->, line width=1, gray] (ymm0) edge (zmm0);

      \visible<2-> {
        \node[right] at (-4, 0) (A) {More/larger registers};
        \node[right] at (2, 0) (B) {More states to manage};
        \draw[->, line width=1, gray] (A) edge (B);
      }
      \visible<3-> {
        \node[right] at (-4, -0.7) {(Intel got something wrong almost everytime)};
      }
    \end{tikzpicture}
  \end{center}
\end{frame}
